\section{Methods}
\label{sec:methods}

% Author: Flo

Although it is hard to make a strict classification of feature-types,
in general, three three different types of features can be distinguished: 

\begin{itemize}
  \item Flat Features
  \item Structured Features
  \item Streaming Features
\end{itemize}

The problem with making a clear classification is that the features themselves,
being regarded simply as numerical data gained by making measurements, have no
structure per se. In fact, the same set of features can be  regarded as flat or 
structured, for example. Dependent on how the underlying problem is modeled,
a certain structure can be assumed. 

The decision, which method should be taken, is therefore dependent on the assumed 
properties of the features. Flat Feature methods take no relationship of
features into account, whereas Structured Feature methods take a given
relationship and use it to preserve structural information.

Since it is not always clear how one feature is related to the other features,
structures are sometimes hard to define and might also give worse results if assumed
wrong. On the other hand, if the structure tends to represent the correct relationships
of the given features, Structured Feature methods tend to outperform Flat
Feature methods (\cite{Tang:14}).

While Flat Feature methods and Structured Feature methods assume a given, finite
feature set, Streaming Feature methods work on an infinite or growing feature
set. Streaming Feature methods are a more general approach, and find
applications in social media.

\input{chapters/methods/flat}
\input{chapters/methods/structured}
\input{chapters/methods/streaming}

	
